---
title: "Your survey data to a simultaneous band in ten lines"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Your survey data to a simultaneous band in ten lines}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", fig.width = 6.5, fig.height = 4)
```

## What `dapcb` does

You have $K$ source populations (countries, districts, schools) whose
curve-valued outcomes — say, an attitude CDF over a response scale, possibly
across several survey waves — were **estimated from complex samples**. You want
a band for a *new* population's curve that is simultaneously valid over the
whole grid, in finite samples, with the *population* as the exchangeable unit.

`dapcb()` returns that band, and decides — via four frozen, target-blind
gates — whether correcting for the survey design noise in the calibration
curves is *reliable* at your $K$. When it is not (which includes every
cross-national survey we know of), the method reduces to an exact clustered
conformal band and tells you why.

## Ten lines

```{r}
library(dapcb)
set.seed(1)
K <- 30; T_ <- 9                                    # 30 countries, 9 thresholds
E <- matrix(rnorm(K * T_, 0, 0.05), K, T_)          # transport-error curves
V <- matrix(abs(rnorm(K * T_, 0.006, 0.001)), K, T_) # design-noise SDs (bootstrap)
center <- pmin(cumsum(abs(rnorm(T_, 0.09, 0.02))), 1) # predicted target curve

fit <- dapcb(E, V, center, alpha = 0.10)
print(fit)
```

The inputs:

- `E` — each row is one source population's transport-error curve
  $E_c(t) = \hat F_c(t) - \tilde F_c(t)$ over the threshold grid (observed
  curve minus its transport prediction);
- `V` — the design-based SD of each curve cell, from your survey's
  stratified-PSU or replicate-weight bootstrap (zeros for a census);
- `center` — the predicted curve for the new population.

## Reading the result

```{r}
fit$selected_branch      # "PCB" | "conservative" | "deconvolution"
fit$coverage_level       # guaranteed lower bound on simultaneous coverage
fit$fallback_reason      # why the aggressive branch was not used
round(cbind(lo = fit$lo, hi = fit$hi), 3)
```

```{r band-plot}
t <- seq_len(length(center))
plot(t, center, type = "l", lwd = 2, ylim = c(0, 1),
     xlab = "threshold", ylab = "CDF", main = "dapcb simultaneous band")
polygon(c(t, rev(t)), c(fit$lo, rev(fit$hi)), border = NA,
        col = grDevices::adjustcolor("steelblue", 0.25))
lines(t, center, lwd = 2)
```

## The guarantee, in one paragraph

The PCB and conservative branches use unstudentized scores, so the $K{+}1$
scores are exchangeable and the order-statistic band is **exact at any $K$**
for the estimated trajectory; because the conservative score dominates the PCB
score pointwise, the two bands are nested and *any* selection between them is
validity-free. The deconvolution branch — which subtracts design noise and is
narrower — carries its own frozen miss budget and can only activate when a
deterministic reliability floor ($K \ge 94$ at the frozen constants) and three
data gates all pass; `coverage_level` reports the resulting guarantee either
way. Details, proofs, and the survey-scale unreachability result are in the
companion paper.

## Cross-language validation

This package is a pure-R port of the reference Python implementation
(`pcb.dapcb` in the replication package). Seven golden cases — spanning all
three branches, a census source, the $K=94$ feasibility boundary, and a tiny-$K$
edge case — are shipped under `inst/golden/` and checked to $10^{-10}$ at
`R CMD check` time.
